hormones

### 2019-10-11 analysis/07_hormones.Rmd
working on side by side

@@

@@

  mycolors <- charcolors

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    scale_fill_manual(values = mycolors) +
    labs(y = myylab, x = NULL) + 
    facet_wrap(~sex, nrow = 2, scale = "free_x")
}

a <- hormonecharplot("estradiol", "E (ng/mL)")
b <- hormonecharplot("testosterone", "T (ng/mL)")
c <- hormonecharplot("cort", "CORT (ng/mL)")
d <- hormonecharplot("progesterone", "PROG (ng/mL)")

e <- hormonecharplot("prolactin", "PRL (ng/mL)")

cd <- plot_grid(e,c,d, nrow = 1)
ab <- plot_grid(a,b, ncol = 1)

plot_grid(cd, ab, rel_widths = c(0.75, 0.25))
```

>>>>

charsexlevels <- c("control female", "control male", "bldg female", "bldg male",  "lay female", "lay male",
                "inc_d3 female", "inc_d3 male", "inc_d9 female", "inc_d9 male",
                "inc_d17 female", "inc_d17 male", "hatch female", "hatch male", 
                "n5 female", "n5 male", "n9 female" , "n9 male")

@@

hormones <- hormones %>%  mutate(treatment.sex = paste(treatment, sex, sep = " ")) 
hormones$treatment.sex <- factor(hormones$treatment.sex, levels = charsexlevels)

@@

  mycolors <- charcolors
  sexcolors <- c("female" = "#969696", "male" = "#525252")

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment, color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_blank(),
          legend.position = "none") +
    scale_fill_manual(values = mycolors) +
    scale_color_manual(values = sexcolors) +
    labs(y = myylab, x = NULL) 
}

hormonecharplot("prolactin", "PRL (ng/mL)")

a <- hormonecharplot("estradiol", "E (ng/mL)")
b <- hormonecharplot("testosterone", "T (ng/mL)")

c <- hormonecharplot("cort", "CORT (ng/mL)")
d <- hormonecharplot("progesterone", "PROG (ng/mL)")

e <- hormonecharplot("prolactin", "PRL (ng/mL)") + theme(legend.position = "right", legend.direction = "horizontal")

cd <- plot_grid(d,c, nrow = 2)
ab <- plot_grid(a,b, nrow = 2)

abcd <- plot_grid(cd,ab, rel_widths = c(0.6,0.4))
plot_grid(e,abcd, ncol = 1)
